### 2019-08-23 lower.tex
Minor fixes

  Now, we claim that given the input $I_1I_2$, every component-respecting DET 
  % (that does not terminate prematurely and never resides in a configuration with components split)
  must produce a sequence $\langle x^{(i)}\rangle$ of length $L = k\cdot \ell - (k-1) - 2 - (\ell-1) - 1$.
  Consider a request $(x^{(i)}, c(x^{(i)}))$.
  If in this configuration at least one singleton component is present (other than the components of $(x^{(i)}, c(x^{(i)}))$), then serving this request is possible (i.e., the perfect partition exists), and hence a singleton node appears as $x^{(i+1)}$ and the sequence continues.
  Otherwise, no perfect partition exists, as we have a component $\{a_1, \ldots, a_{k-1}\}$ of size $k-1$.

  Hence, the length of a sequence $\langle x^{(i)}\rangle$ is closely related to the number of singleton components.
  Before the arrival of the first request from $I_2$, the number of singleton components is $L + (\ell-1) + 1$, and after serving the last request, the number of singleton components is $1$.
  %Every node $x^{(i)}$ must be a singleton component, otherwise DET resides in a configuration with components split (and such DETs either leave such configuration eventually or issue an infinite cost).
  After each request, we join this singleton component with another component.
  This join decreases the number of singleton components by either $1$ or $2$: if we join two singletons $\{v^C_0\}, \{v^C_1\}$ (there are $\ell-1$ such joins: for all clusters but $A$), then the number of singletons decrease by $2$, and it decreases by $1$ otherwise.
  We conclude that the number of requests $\langle x^{(i)}\rangle$ to decrease the number of singletons to $1$ is $L$.

>>>>

  Now, we claim that given the input $I_1I_2$, every component-respecting DET 
  % (that does not terminate prematurely and never resides in a configuration with components split)
  must produce a sequence $\langle x^{(i)}\rangle$ of length $L = k\cdot \ell - (k-1) - 2 - (\ell-1) - 1$.
  Consider a request $(x^{(i)}, c(x^{(i)}))$.
  If in this configuration at least one singleton component is present (other than the components of $(x^{(i)}, c(x^{(i)}))$), then serving this request is possible (i.e., the perfect partition exists), and hence a singleton node appears as $x^{(i+1)}$ and the sequence continues.
  Otherwise, no perfect partition exists, as we have a component $\{a_1, \ldots, a_{k-1}\}$ of size $k-1$ and it can only be complemented by a singleton component.

  \maciek{A candidate for auxiliary lemma: intuitions before the claim, then the formal formulation, and a rewrite of the argument from this paragraph}
  Hence, the length of a sequence $\langle x^{(i)}\rangle$ is closely related to the number of singleton components.
  Before the arrival of the first request from $I_2$, the number of singleton components is $L + (\ell-1) + 1$, and after serving the last request, the number of singleton components is $1$.
  %Every node $x^{(i)}$ must be a singleton component, otherwise DET resides in a configuration with components split (and such DETs either leave such configuration eventually or issue an infinite cost).
  After each request, we join this singleton component with another component.
  This join decreases the number of singleton components by either $1$ or $2$: if we join two singletons $\{v^C_0\}, \{v^C_1\}$ (there are $\ell-1$ such joins: for all clusters but $A$), then the number of singletons decrease by $2$, and it decreases by $1$ otherwise.
  We conclude that the number of requests $\langle x^{(i)}\rangle$ to decrease the number of singletons to $1$ is $L$.
